---
title: "Iris Correlation Explorer- Coursera Developing Data Products"
output: slidy_presentation
author: "pankaj sharma"
---

## Scatterplot Matrix with GGally

* A scatterplot matrix is a series of scatterplots organized in a grid and often used to describe the relationship between different variables. 
* These plots can range over different degrees of complexity, from merely plotting correlations between variablesup to histograms and kernel density plots of distributions that incorporate other variable metadata


## Plotting Options

**Argument**  |  **Plots Available**
------------- | -----------------------
continuous    |"points","smooth","density","cor","blank"
discrete      |"facetbar", "ratio", "blank"
combo         |"box", "dot", "facethist","facetdensity", "denstrip", "blank"

### Variable combination

- continuous versus.continuous
- discrete versus. discrete
- continuous versus. discrete


## R Code and Output

```{r}
summary(iris)
```

## Correlation  Plot

```{r, echo=FALSE,warning=FALSE}
require(GGally)
ggpairs(iris, upper=list(continuous="density"),
lower=list(continuous="smooth",combo="facetdensity"),
color="Species")
```

